---
title: "Home Prices EDA and Machine Learning"
output: html_document

---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Add Libraries
```{r, include=FALSE}
library(data.table)
library(ggplot2)
library(ggthemes)
library(glmnet)
library(plotly)
library(MASS)
library(caret)
library(leaps)
library(tibble)
library(magrittr) 
library(dplyr)
library(tidyverse)
library(scales)
library(tree)
library(randomForest)
library(rpart)
library(rpart.plot)

theme_set(theme_bw())
```

#### Load in dataset
```{r}
#install.packages('bit64')
setwd('/Users/petermankiewich/Dropbox/BU/BA810/group_project')
Price <- fread("trainPrice.csv")
#Price <- fread("/Users/paulademacker/Documents/USA/Boston U/2. term/BA810/Team Project/trainPrice.csv")
```

#### First few rows
We can see that we have a total of 25 features in the dataset
```{r}
head(Price, 5)
```

#### Structure of the dataset
There are a total of 1,601,458 observations
```{r}
str(Price)
transform(Price, transaction_real_price = as.numeric(transaction_real_price))
#summary(Price)
```


### Cleaning the Data

#### view the count of null values in each column
The feature, total_parking_capacity_in_site has the largest number of null values (91813)
```{r}
Price[, lapply(.SD, function(x) sum(is.na(x)))]
```
#### View all unqiue values present in columns
```{r}
unique(Price$heat_type)
```
##### How many are empty strings?
```{r}
Price[heat_type == ''][, .N]
```

##### We can remove these empty string and dash values to create dummy variables later
```{r}
Price <- Price[heat_type != '']
```
```{r}
Price[heat_fuel == ''][, .N]
```
```{r}
Price[heat_fuel == '-'][, .N]
```
```{r}
Price <- Price[heat_fuel != '']
```
```{r}
Price <- Price[heat_fuel != '-']
```

#####View the unique values in other columns
```{r}
unique(Price$bathroom_count)
```
```{r}
unique(Price$city)
```
```{r}
unique(Price$room_count)
```
```{r}
unique(Price$front_door_structure)
```

##### Count of values that are dashes
```{r}
Price[front_door_structure == '-'][, .N]
```

##### Count of values that are empty strings
```{r}
Price[front_door_structure == ''][, .N]
```

##### We can remove these empty string values to create dummy variables later
```{r}
Price <- Price[front_door_structure != '']
```

##### We can remove these empty dash values to create dummy variables later
```{r}
Price <- Price[front_door_structure != '-']
```

##### View unique year of completion values
```{r}
unique(Price$year_of_completion)
```

#### Drop rows room_count as 8
After examining the dataset, we determined that this was an outlier since only a very small number of apartments were shown as having 8 rooms
```{r}
Price <- Price[room_count != 8]
```

#### Remove all rows that have missing values
There are a total of 1601458 million observations, and we will be removing less than 100,000 of them.
We can confirm that rows were removed using .N (the number of observations)
```{r}
Price <- na.omit(Price)
Price[, .N]
```

#### Set city and room count as factor
```{r}
# Price <- Price[, city:=as.factor(city)]
# Price <- Price[, room_count:=as.factor(room_count)]
# Price <- Price[, bathroom_count:=as.factor(bathroom_count)]
#Price <- Price[, transaction_year_month := as.POSIXct(transaction_year_month, format='%Y%m')]
#Price <- Price[, year_of_completion := as.Date(year_of_completion, format='%Y')]

str(Price)
```


##### Create dummy variables for use in later ML steps
We will convert transaction_date, heat_type, heat_fuel, and front_door_structure
```{r}
Price <- Price[transaction_date == "1~10", transaction_date:=0]
Price <- Price[transaction_date == "11~20", transaction_date:=1]
Price <- Price[transaction_date == "21~30", transaction_date:=2]
Price <- Price[transaction_date == "21~28", transaction_date:=2]
Price <- Price[transaction_date == "21~29", transaction_date:=2]
Price <- Price[transaction_date == "21~31", transaction_date:=2]
Price[,transaction_date := as.numeric(transaction_date)]

Price <- Price[heat_type == "individual", heat_type:=0]
Price <- Price[heat_type == "central", heat_type:=1]
Price <- Price[heat_type == "district", heat_type:=2]
Price[,heat_type := as.numeric(heat_type)]

Price <- Price[heat_fuel == "gas", heat_fuel:=0]
Price <- Price[heat_fuel == "cogeneration", heat_fuel:=1]
Price[,heat_fuel := as.numeric(heat_fuel)]

Price <- Price[front_door_structure == "corridor", front_door_structure:=0]
Price <- Price[front_door_structure == "stairway", front_door_structure:=1]
Price <- Price[front_door_structure == "mixed", front_door_structure:=2]
Price[,front_door_structure := as.numeric(front_door_structure)]

Price[,transaction_real_price := as.numeric(transaction_real_price)] 
Price[,address_by_law := as.numeric(address_by_law)]
```


#### Barchart showing real price and city
```{r}
ggplot(Price, aes(x=as.factor(city), y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```

#### Barchart showing real price and room count
```{r}
ggplot(Price, aes(x=room_count, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```
#### Barchart showing real price and front_door_structure
```{r}
ggplot(Price, aes(x=front_door_structure, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```

#### Barchart showing real price and heat_fuel
```{r}
ggplot(Price, aes(x=heat_fuel, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```
#### Barchart showing real price and heat_type
```{r}
ggplot(Price, aes(x=heat_type, y = transaction_real_price)) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```





#### Plotly Map showing locations of apartments
We can see that all of the apartments are either in Seoul or Busan
```{r}
# fig <- head(Price, 100000)
# fig <- fig %>%
#   plot_ly(
#     lat = ~latitude,
#     lon = ~longitude,
#     #marker = list(color = "fuchsia"),
#     color = Price[,"transaction_real_price"],
#     type = 'scattermapbox',
#     hovertext = Price[,"transaction_real_price"]) 
# fig <- fig %>%
#   layout(
#     mapbox = list(
#       style = 'open-street-map',
#       zoom =2.5,
#       center = list(longitude = 35.963911, latitude = 127.919770))) 
# 
# fig
```






## Linear Regression
#### Randomize the rows
```{r}
set.seed(42)
rows <- sample(nrow(Price))
Price <- Price[rows, ]
```



## Forward Selection
```{r}

# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
step.model <- train(transaction_real_price ~., data = dd_train,
                    method = "leapForward", 
                    tuneGrid = data.frame(nvmax = 1:24),
                    trControl = train.control
                    )
step.model$results
```
```{r}
step.model$bestTune
summary(step.model$finalModel)
```

## Backward selection
```{r}

# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
step.model <- train(transaction_real_price ~., data = dd_train,
                    method = "leapBackward", 
                    tuneGrid = data.frame(nvmax = 1:24),
                    trControl = train.control
                    )
step.model$results
```


```{r}
step.model$bestTune
summary(step.model$finalModel)
```



